Web Service Community \\ Learning

### 2014-06-15 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Recent work have emphasized on motivation and benefits of communities of web services [references]. This is due to the fact that communities facilitate discovery of web services, improve the quality of service, and help individual services find better market share and opportunities. The challenge is then community development, which is finding the right web service for the community, satisfying all web services and community coordinators involved within the community. This is also a challenge from individual web service side in the sense that a web service seeks for communities to interact with and obtain best outcome. Towards addressing these issues, there have been a number of proposals. Some of these works propose complex models on demand algorithms [3way, coopchina, ourwork] to effectively find target points. But they have to simplify the algorithm by limited parameters in order to make it feasible and algorithm executable. The simplifications problem some times negatively influences the outcome in the sense that simplifying the constraints may cause ignoring important aspects of the problem. For example [coopchina] proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work instead of complex shapely-value. This model considers gain for all subset of agents working together, which basically ignores the most important criteria of finding optimal group. Other category of related work exists which they do not focus on all parties involved within the community [2player]. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in real world hurting the decision making performance.

>>>>

Recent work have emphasized on motivation and benefits of communities of web services [references]. This is due to the fact that communities facilitate discovery of web services, improve the quality of service, and help individual services find better market share and opportunities. The challenge is then community development, which is finding the right web service for the community, satisfying all web services and community coordinators involved within the community. This is also a challenge from individual web service side in the sense that a web service seeks for communities to interact with and obtain best outcome. Towards addressing these issues, there have been a number of proposals. Some of these works propose complex models on demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points. But they have to simplify the algorithm by limited parameters in order to make it feasible and algorithm executable. The simplifications problem some times negatively influences the outcome in the sense that simplifying the constraints may cause ignoring important aspects of the problem. For example \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work instead of complex shapely-value. This model considers gain for all subset of agents working together, which basically ignores the most important criteria of finding optimal group. Other category of related work exists which they do not focus on all parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in real world hurting the decision making performance.
